Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex

>>>>

In general, a volunteer-based distributed evolutionary computation
system based on the browser is simply a client-server architecture
whose client is, or can be, embedded in the browser via
JavaScript. All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} has two parts:\begin{enumerate}
\item A REST server, that is, a server that includes several remote
  requests for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it. It also peforms logging
  duties, but is basically a very lightweight and hign performance
  data store \cite{jj:idc:lowcost}.
\item A client that includes the evolutionary algorithm as 
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request).
\end{enumerate}

The researcher only has to change a function to solve a different
problem, in this case the classical Trap function has been
used. JavaScript is a functional language and
